---
title: "EDLD_proj_MAPS"
author: "Kavya Mudiam"
date: "2/13/2021"
output: html_document
---

```{r}
library(rio)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(colorblindr)
library(lubridate)
install.packages("plotly")
library(plotly)
```

```{r}
here::here()
df <- import("data/df_times_021321_wide.csv")
df_l <- import("data/df_times_021321.csv")
str(df)

names(df)
df <- df %>% 
  mutate(participant_id = factor(participant_id),
         device_id = factor(device_id),
         TimePoint = factor(TimePoint),
         TimeWith = factor(TimeWith)) 
    # rename("Sad" = `sad`, "Stressed" = `stressed`, "Anxious" = `anxious`, "Supported" = `supported`, "Happy" = `happy`, "Angry" = `angry`, "Scared" = `scared`, "Calm" =  `calm`, "Confident" = `confident`, "Lonely" = `lonely`, "Rejected" = `rejected`, "Included" = `included`)

str(df_l)
df_l <- df_l %>% 
  mutate(participant_id = factor(participant_id),
         device_id = factor(device_id),
         TimePoint = factor(TimePoint),
         question_id = factor(question_id),
         string_answer = factor(string_answer))
```

#cut offs for MFQ, SCARED
https://jrcalabrese.github.io/clinical_cutoff.html

*5 item SCARED cutoffs*
*https://www.sciencedirect.com/science/article/pii/S0890856709632378?via%3Dihub
> Based on the sensitivity and specificity of the 5-item scale, a cutoff of 3 can be used for discriminating anxiety from nonanxiety

*MFQ cut offs*
*no 

```{r}
df <- df %>% 
  mutate(scared_sev = if_else(scared>3, 1, 0),
         scared_sev = factor(scared_sev),
         mfq_sev = if_else(mfq > 8, 1, 0),
         mfq_sev = factor(mfq_sev))

df_l <- df_l %>% 
    mutate(scared_sev = if_else(scared>3, 1, 0),
         scared_sev = factor(scared_sev),
         mfq_sev = if_else(mfq > 8, 1, 0),
         mfq_sev = factor(mfq_sev))

hist(df$scared)
hist(df$mfq)
df %>% 
  ggplot(aes(mfq_sev)) +
  geom_bar(aes(y = stat(count)))



```

#just visualizing the data sort of generally 
```{r}
df_l <- df_l %>% 
  group_by(question_id) %>% 
  mutate(mean_response = mean(int_answer, na.rm = T))

ggplot(df_l, aes(question_id, int_answer))+
  geom_bar(stat = "summary", fill = "pink") +
  labs(title = "Self-reported mood scores averaged across all timepoints",
       x= "Mood",
       y= "Severity") +
  expand_limits(y = c(0,100))

#only include a few of the questions
df_l %>% 
  filter(question_id == c("happy", "sad", "stressed", "anxious", "supported")) %>% 
  ggplot(aes(x= question_id, int_answer))+
  geom_bar(stat = "summary", fill = "pink")+
  labs(title = "Self-reported mood scores averaged across all timepoints",
       x= "Mood",
       y= "Severity") +
  expand_limits(y = c(0,100))

#tried a scatterplot for fun - EW, NOT FUN
ggplot(df_l, aes(x = TimePoint, y = int_answer, 
                 shape = question_id)) +
  geom_point()

range(df$anxious, na.rm = T)

summary(df)
```

9.3 Bubble charts -- https://rkabacoff.github.io/datavis/Other.html#Bubble
#Bubble charts, TimeWith x Mood
```{r}
df_bub <- df %>% 
  select(participant_id, TimeWith, scared_sev, happy, sad, stressed, anxious, supported) %>% 
  pivot_longer(cols = c(happy, sad, stressed, anxious, supported),
               values_drop_na = T) %>% 
  mutate(name = factor(name),
         name = fct_relevel(name, c("sad", "stressed", "anxious", "supported", "happy"))) %>%
  filter(TimeWith != "")


df_bub <- df_bub %>% 
  group_by(TimeWith, name) %>% 
  mutate(mean = mean(value, na.rm = T)) #can I include this all within the ggplot function?

# df_bub_mean <- df_bub %>%
#   dplyr::select(TimeWith, name, mean) %>%
#   group_by(TimeWith, name) %>%
#   unique()
  
summary(df_bub$TimeWith)

ggplot(df_bub, 
       aes(x = TimeWith, y = name, size = mean)) +
  geom_point(aes(fill = name,
                 color = name),
             shape = 21) + #, show.legend = F) +
    scale_fill_OkabeIto() +
    scale_color_OkabeIto() +
  theme_minimal() +
  theme(legend.position = "none",
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_blank()) +
  scale_size_continuous(range = c(1, 25)) +
  geom_text(aes(label = round(mean,0)), size = 4) +
  labs(title = "Severity of Emotion After Spending Time Alone or With Certain People",
       x = "Time Spent With",
       y = " ") +
  scale_x_discrete(labels = c('Alone','Co-Students','Co-Workers', "Family", "Friends", "Partner")) +
  scale_y_discrete(labels = c("Sad", "Stressed", "Anxious", "Supported", "Happy"))
```
#Bubble Plot, Alone v Together x Mood
```{r}
df_bub <- df_bub %>% 
  mutate(with = ifelse(TimeWith != "alone", "Not Alone", "Alone")) %>% 
  group_by(name, with) %>% 
  mutate(mean_with = mean(value, na.rm = T),
         with = factor(with),
         )

ggplot(df_bub, 
       aes(x = with, y = name, size = mean_with)) +
  geom_point(aes(fill = name,
                 color = name),
             shape = 21) + 
    scale_fill_OkabeIto() +
    scale_color_OkabeIto() +
  theme_minimal() +
  theme(legend.position = "none",
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_blank()) +
  scale_size_continuous(range = c(1, 25)) +
  geom_text(aes(label = round(mean_with,0)), size = 4) +
  labs(title = "Severity of Emotion After Spending Time Alone or Not Alone",
       x = "",
       y = "") +
    scale_y_discrete(labels = c("Sad", "Stressed", "Anxious", "Supported", "Happy"))

```

#Bubble plots with baseline anxiety
```{r}
df_bub <- df_bub %>% 
  group_by(name, TimeWith, scared_sev) %>% 
  mutate(mean_scared = mean(value, na.rm = T)) %>% 
  drop_na(scared_sev)


# ggplot(df_bub, 
#        aes(x = TimeWith, y = name, size = mean_scared)) +
#   geom_point(aes(fill = name,
#                  color = name),
#              shape = 21) +
#   facet_wrap(~scared_sev) #NEED TO DROP NA VALUE!!!!!! 

anxsev.labs <- c("No Anxiety at Baseline", "Anxiety at Baseline")
names(anxsev.labs) <- c("0", "1")


ggplot(df_bub, 
       aes(x = TimeWith, y = name, size = mean_scared)) +
  geom_point(aes(fill = name,
                 color = name),
             shape = 21) + 
  facet_wrap(~scared_sev,
             labeller = labeller(scared_sev = anxsev.labs)) +
    scale_fill_OkabeIto() +
    scale_color_OkabeIto() +
  theme_minimal() +
  theme(legend.position = "none",
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_blank(),
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
  scale_size_continuous(range = c(1, 25)) +
  geom_text(aes(label = round(mean_scared,0)), size = 4) +
  labs(title = "Severity of Emotion AMong Anxious and Non-Anxious Individuals After Spending Time Alone or With Certain People",
       x = "",
       y = " ") +
  scale_x_discrete(labels = c('Alone','Co-Students','Co-Workers', "Family", "Friends", "Partner")) +
  scale_y_discrete(labels = c("Sad", "Stressed", "Anxious", "Supported", "Happy"))

df_bub %>% 
  group_by(scared_sev) %>% 
  count()

# df_bub %>% 
#   count(scared_sev) #gives me a different count value than above
```

#Lineplot with time x sadness depending on baseline ____

```{r}
df %>% 
select(TimePoint) %>% 
mutate(TimePoint = as.integer(TimePoint)) %>% 
  range()

df_line <- df %>% 
  group_by(TimePoint, scared_sev) %>% 
  mutate(mean_sad = mean(sad, na.rm = T)) %>% 
  filter(scared_sev != "")
df_line <- df %>% 
  group_by(TimePoint, mfq_sev) %>% 
  mutate(mean_sad_mfq = mean(sad, na.rm = T)) %>% 
  drop_na(mfq_sev)

df_line %>% 
  group_by(scared_sev) %>% 
  count()
df_line %>% 
  group_by(TimePoint) %>% 
  count()

df_line %>% 
  group_by(mfq_sev) %>% 
  summary()

df_line %>% 
  group_by(mfq_sev,TimePoint) %>% 
  count() #After a certain point, there's only one data point for later timepoints. Should I stop once n gets below 5?


ggplot(df_line, mapping = aes(as.numeric(TimePoint), mean_sad)) +
  geom_line(aes(color = scared_sev)) +
  geom_point(shape=21, aes(color=scared_sev, fill = scared_sev), size=2) +
  labs(x = "Time Point",
       y = "Sadness Severity") +
  scale_color_OkabeIto() +
  annotate("text", label = "No Baseline Anxiety", x = 28, y = 50, color = "orange") +
  annotate("text", label = "Baseline Anxiety", x = 42, y = 40, color = "turquoise") +
  theme_minimal() +
  theme(legend.position = "none",
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_blank())


sad_by_dep <- ggplot(df_line, mapping = aes(as.numeric(TimePoint), mean_sad_mfq)) +
  geom_line(aes(color = mfq_sev)) +
  geom_point(shape=21, aes(color=mfq_sev, fill = mfq_sev), size=2) +
  labs(x = "Time Point",
       y = "Sadness Severity",
       title = "Average Severity of Sadness Between Depressed and Non-Depressed Adolescents Over Time") +
  scale_color_OkabeIto() +
  annotate("text", label = "Not Depressed at Baseline", x = 36.5, y = 12, color = "orange") +
  annotate("text", label = "Depressed at Baseline", x = 44, y = 45, color = "turquoise") +
  theme_minimal() +
  theme(legend.position = "none",
        #panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_blank()) + 
  scale_x_continuous(breaks = seq(0, 60, by = 10))

ggplotly(sad_by_dep)
  
```

